INTELLIGENT SYSTEMS

### 2021-04-15 papers/paper_7.tex
finish slides paper7

To test the efficiency of the methods, several images belonging to a 
BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
and $n_2$) with different ratios $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
state of the art.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
        \hline        
        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
        \hline 
        \hline
        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
        \hline
        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
    \label{indexCompare}
\end{table}

>>>>

To test the efficiency of the methods, several images belonging to a 
BSDS100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
and $n_2$) with different ratios $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
state of the art.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
        \hline        
        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
        \hline 
        \hline
        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
        \hline
        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
    \label{indexCompare}
\end{table}

### 2021-04-15 slides/slides_paper7.tex
finish slides paper7

>>>>

\begin{frame}{EXPERIMENTAL RESULTS - Gaussian mixed-noise}
    The indexs used to estimate the quality of the restructured images are 
    the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural Similarity Index} 
    (SSIM). The results obtained by comparing different methods with the 
    proposed, in image reconstruction and Gaussian mixed-noise removal, one 
    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The set test images were taken from 
    the BSDS100 dataset.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.8\linewidth]{images/paper7/GMN comparison.png}
        \centering
        \caption{Image reconstruction under Gaussain mixture noise comparison.}
        \label{fig:GMNComp}
    \end{figure}

    \begin{table}[htbp]
        \centering
        \begin{adjustbox}{width=0.8\textwidth}
        \begin{tabular}{|c||ccc|ccc|ccc|}
            \hline
                & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
            \hline        
            $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
            \hline 
            \hline
            \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
            & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
            \hline
            \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
            & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
            \hline
            \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
            & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
        \label{indexCompare}
    \end{table}

\end{frame}

\begin{frame}{EXPERIMENTAL RESULTS - Gaussian random-noise}
    As for the reconstruction of an image affected by random noise, also 
    called salt and pepper noise, the results obtained from the comparison of 
    different methods are visible in figure \ref{fig:saltComp} and in table \ref{GNPINIndex}. As in the previous 
    experiment, the indexs are calculated by changing the mixed-ratio $r$ and 
    standard deviation $\sigma$ values.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.7\linewidth]{images/paper7/salt.png}
        \centering
        \caption{Image reconstruction under Gaussain noise plus random-valued noise comparison.}
        \label{fig:saltComp}
    \end{figure}

    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=0.7\textwidth}
        \begin{tabular}{|c||ccc|ccc|ccc|}
            \hline
                & \multicolumn{3}{c||}{$\sigma_1=5$} & \multicolumn{3}{c||}{$\sigma_1=10$} & \multicolumn{3}{c||}{$\sigma_1=15$}\\
            \hline        
            $r\rightarrow$ & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3\\
            \hline 
            \hline
            \multirow{2}{*}{Noisy} & 18.76 & 15.76 & 14.04 & 18.43 & 15.61 & 13.95 & 17.94 & 15.38 & 13.81\\
            & 0.3545 & 0.2290 & 0.1662 & 0.3313 & 0.2216 & 0.1626 & 0.3040 & 0.2109 & 0.1571\\
            \hline
            \multirow{2}{*}{Two-phase\cite{0884882828}} & 25.40 & 24.77 & 24.13 & 24.34 & 23.94 & 23.45 & 23.32 & 23.02 & 22.67\\
            & 0.6599 & 0.6313 & 0.5957 & 0.5116 & 0.4914 & 0.4655 & 0.4224 & 0.4058 & 0.3854\\
            \hline
            \multirow{2}{*}{ACWMF+K-SVD \cite{0884882844}\cite{0884882813}} & 26.07 & 25.27 & 24.54 & 25.50 & 24.91 & 23.13 & 24.64 & 24.19 & 23.67\\
            & 0.7130 & 0.6761 & 0.6333 & 0.5902 & 0.5613 & 0.5291 & 0.4855 & 0.4625 & 0.4414\\
            \hline    
            \multirow{2}{*}{LSM-NLR \cite{0884882826}} & 29.48 & 26.97 & 24.55 & 29.43 & 27.08 & 24.43 & 28.51 & 26.06 & 23.98\\
            & 0.6548 & 0.5774 & 0.4982 & 0.6420 & 0.5646 & 0.4770 & 0.6282 & 0.5458 & 0.4643\\
            \hline
            \multirow{2}{*}{$l_1-l_0$\cite{0884882829}} & 30.45 & 27.75 & 25.95 & 28.45 & 26.59 & 25.34 & 27.33 & 25.69 & 24.55\\
            & 0.8962 & 0.7911 & 0.7312 & 0.7539 & 0.6748 & 0.6293 & 0.6793 & 0.6010 & 0.5744\\
            \hline
            \multirow{2}{*}{Proposed} & \bfseries{31.06} & \bfseries{30.44} & \bfseries{27.66} & \bfseries{30.97} & \bfseries{29.5} & \bfseries{27.41} & \bfseries{29.74} & \bfseries{28.09} & \bfseries{25.73}\\
            & \bfseries{0.9214} & \bfseries{0.9157} & \bfseries{0.8497} & \bfseries{0.8943} & \bfseries{0.8749} & \bfseries{0.8316} & \bfseries{0.8530} & \bfseries{0.8222} & \bfseries{0.7750}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Average PSNR and SSIM values on one image of some methods.}
        \label{GNPINIndex}
    \end{table}
\end{frame}

\begin{frame}{CONCLUSION}
    Even reaching good performances, the proposed method does not always 
    manage to obtain better results than those of competing methods. 
    However, the average of the PSNR index achieved is the highest (Fig. \ref{fig:cropRes}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper7/crop.png}
        \centering
        \caption{Cropped real noisy images.}
        \label{fig:crop}
    \end{figure}

    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
        \centering
        \caption{PSNR result of different methods on cropped real noisy images.}
        \label{fig:cropRes}
    \end{figure}

\end{frame}
